Adaption of the Chumbley Score to matching of bullet striation marks

### 2018-02-05 doc/paper.Rmd
cleaning files

```{r wo120-profile, fig.width = 6, fig.height=4, fig.cap="The figure shows the Type II error for different validation window sizes and different chosen nominal alpha levels when the size of the optimization window = 120"}
wo120_profile <- errors2 %>% filter(wo==120, coarse == 0.25) %>% 
  #gather(type, error, actual:beta) %>% 
  gather(type, error, beta) %>% 
  ggplot(aes(x = wv, y = error, colour = factor(alpha)))  + 
  geom_line() + geom_point() + facet_wrap(~type, scales="free") +
    theme_bw()+ 
  theme(legend.position="bottom") + ggtitle("Profile" , subtitle = "Varying validation window sizes, Optimization window = 120, Coarseness = 0.25")

>>>>

```{r wo120-profile, fig.width = 6, fig.height=4, fig.cap="The figure shows the Type II error for different validation window sizes and different chosen nominal alpha levels when the size of the optimization window = 120", eval = FALSE}
wo120_profile <- errors2 %>% filter(wo==120, coarse == 0.25) %>% 
  #gather(type, error, actual:beta) %>% 
  gather(type, error, beta) %>% 
  ggplot(aes(x = wv, y = error, colour = factor(alpha)))  + 
  geom_line() + geom_point() + facet_wrap(~type, scales="free") +
    theme_bw()+ 
  theme(legend.position="bottom") + ggtitle("Profile" , subtitle = "Varying validation window sizes, Optimization window = 120, Coarseness = 0.25")
